---
title: "Causal verbs and responsibility"
author: "Cici Hou, David Rose & Ellen Markman"
date: "`r Sys.time()`"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 6
    toc_float: true
    theme: cosmo
    highlight: tango
---

# Load packages

```{r eval=TRUE, include=FALSE, message=FALSE, warning=FALSE}

library("tidytext")
library("xtable")          # for saving tables
library("janitor")         # for cleaning variable names
library("emmeans")         # for comparing means
library("brms")            # for Bayesian data analysis
library("patchwork")       # for combining figures
library("knitr")           # for knitting 
library("marginaleffects") # for marginal effects
library("ggtext")          # for adding text to figures
library("grid")            # for annotation custom
library("RColorBrewer")    # for colors 
library("ggtext")          # for text in ggplot 
library("tidyverse")       # for everything else
```

# Settings

```{r message=FALSE, warning=FALSE}

# set theme 
theme_set(theme_classic())

# sum coding
options(contrasts = c("contr.sum","contr.poly"))

# suppress grouping warning 
options(dplyr.summarise.inform = F)
```

# Helper functions 

```{r}

# for color gradients
make_gradient = function(deg = 45, n = 100, cols = blues9) {
  cols = colorRampPalette(cols)(n + 1)
  rad = deg / (180 / pi)
  mat = matrix(
    data = rep(seq(0, 1, length.out = n) * cos(rad), n),
    byrow = TRUE,
    ncol = n
  ) +
  matrix(
    data = rep(seq(0, 1, length.out = n) * sin(rad), n),
    byrow = FALSE,
    ncol = n
  )
  mat = mat - min(mat)
  mat = mat / max(mat)
  mat = 1 + mat * n
  mat = matrix(data = cols[round(mat)], ncol = n)
  grid::rasterGrob(
    image = mat,
    width = unit(1, "npc"),
    height = unit(1, "npc"),
    interpolate = TRUE
  )
}

# softmax function
softmax = function(x, beta = 1) {
  return(exp(x * beta) / sum(exp(x * beta)))
}

```

# EXPERIMENT 1: CHAIN CASES
## DATA
### Read in data
```{r}

df.exp1_children = read_csv("../../data/exp1_child_clean.csv") 

df.exp1_children = df.exp1_children %>%
  select(scenario_order, gender_order, question, participant_age, age_float, distal, proximal, scenario, response_id, gender, lan_spoken)

```
### Demographics

```{r message=FALSE, warning=FALSE}
# gender
df.exp1_children %>%
  group_by(gender) %>%
  summarise(n = n_distinct(response_id)) %>%
  print()

# language spoken
df.exp1_children %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(response_id)) %>%
    print()
```

## STATS

### Bayesian Model
```{r message=FALSE, warning=FALSE}
df.exp1_children_different = df.exp1_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))

df.exp1_children_both = df.exp1_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both") 


 df.exp1_children_both = df.exp1_children_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.exp1_children_both %>% 
              mutate(difference = 0)) 

df.exp1_children_new = df.exp1_children_different %>% 
  bind_rows(df.exp1_children_both) 
  
df.model = df.exp1_children_new %>% 
  mutate(
    # Convert to factor explicitly
    question = as_factor(question),
    question = fct_relevel(question, 
                           "fault",   
                           "cause", # second
                           "lexical")  # etc...
  )

fit.brm.chain.children = brm(formula = difference ~ 1 + question * age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/chain_cause_children_difference") 

fit.brm.chain.children 
```

### Follow-up analysis 

```{r}
# effect of question 
fit.brm.chain.children %>% 
  emmeans(spec = pairwise ~ question, 
          type = "response")

# effect of age
fit.brm.chain.children %>%
  avg_slopes(variable = "age_float",
             type = "link")
  
# interaction effect 
fit.brm.chain.children %>% 
  emtrends(specs = pairwise ~ question,
           var = "age_float")
```

### Means and Confidence Interval  

```{r}

df.exp1_children_new %>% 
  group_by(question) %>% 
  summarise(
    mean = mean(difference),
    ci_lower = mean_cl_normal(difference)$ymin,
    ci_upper = mean_cl_normal(difference)$ymax
  )

```

## PLOTS

```{r}
df.model = df.exp1_children_new %>% 
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))

fit.brm.chain.difference = brm(formula = difference ~ 1 + question*age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     cores = 8,
                     file = "cache/fit.brm.chain.difference")

fit.brm.chain.difference


df.data = expand_grid(age_float = seq(3, 9, 0.1),
                      question = c("cause", "lexical", "fault"))

df.prediction = fit.brm.chain.difference %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  clean_names()

df.linear = df.model %>% 
  mutate(participant_age = factor(participant_age, 
                            levels = c(3, 4, 5, 6, 7, 8, 9), 
                            labels = c("3", "4", "5", "6", "7", "8", "9")))

df.means = df.linear %>% 
  group_by(participant_age, question) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(participant_age = as.numeric(as.character(participant_age)))

p2 = ggplot(mapping = aes(x = age_float, 
                     y = difference,
                     color = question)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = participant_age,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = FALSE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.5)) +
  ylab(element_blank()) +
  scale_fill_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), breaks=c("cause", "lexical", "fault")) +
  scale_color_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), breaks=c("cause", "lexical", "fault")) +
  scale_shape_manual(values = c(23, 21, 24)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n proximal", "75%", "50%", "75%", "100% \n distal"),
                     limits = c(0, 1)) + 
  scale_x_continuous(name = "Age",
                     breaks = 3:9,
                     labels = c("3", "4", "5", "6", "7", "8", "9")) +
  theme(plot.title = element_text(hjust = 1),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        legend.title = element_blank(),
        text = element_text(size = 20))

p2
```

# EXPERIMENT 2: ABSENCE CASES
## DATA
### Read in data
```{r}
df.exp2_children = read_csv("../../data/exp2_child_clean.csv") 

df.exp2_children = df.exp2_children %>%
  select(scenario_order, gender_order, question, participant_age, age_float, direct, absent, scenario, response_id, gender, lan_spoken)
```
### Demographics

```{r message=FALSE, warning=FALSE}
# gender
df.exp2_children %>%
  group_by(gender) %>%
  summarise(n = n_distinct(response_id)) %>%
  print()

# language spoken
df.exp2_children %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(response_id)) %>%
    print()
```

## STATS

### Bayesian Model
```{r message=FALSE, warning=FALSE}
df.exp2_children_different = df.exp2_children %>%
  mutate(response_pattern = case_when(
    absent == 1 & direct == 1 ~ "both",
    absent == 0 & direct == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = absent - direct,
        difference = recode(difference, `-1` = 0))

df.exp2_children_both = df.exp2_children %>%
  mutate(response_pattern = case_when(
    absent == 1 & direct == 1 ~ "both",
    absent == 0 & direct == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both") 


 df.exp2_children_both = df.exp2_children_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.exp2_children_both %>% 
              mutate(difference = 0)) 

df.exp2_children_new = df.exp2_children_different %>% 
  bind_rows(df.exp2_children_both) 
  
df.model = df.exp2_children_new %>% 
  mutate(
    # Convert to factor explicitly
    question = as_factor(question),
    question = fct_relevel(question, 
                           "fault",   
                           "cause", # second
                           "lexical")  # etc...
  )

fit.brm.absence.children = brm(formula = difference ~ 1 + question * age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/absence_cause_children_difference") 

fit.brm.absence.children 
```

### Follow-up analysis 

```{r}
# effect of question 
fit.brm.absence.children %>% 
  emmeans(spec = pairwise ~ question, 
          type = "response")
# 
# # effect of age
# fit.brm.absence.children %>%
#   avg_slopes(variable = "age_float",
#              type = "link")
  
# interaction effect 
fit.brm.absence.children %>% 
  emtrends(specs = pairwise ~ question,
           var = "age_float")
```

### Means and Confidence Interval  

```{r}

df.exp2_children_new %>% 
  group_by(question) %>% 
  summarise(
    mean = mean(difference),
    ci_lower = mean_cl_normal(difference)$ymin,
    ci_upper = mean_cl_normal(difference)$ymax
  )

```

## PLOTS

```{r}
df.model = df.exp2_children_new %>% 
  mutate(difference = absent - direct,
        difference = recode(difference, `-1` = 0))

fit.brm.absence.difference = brm(formula = difference ~ 1 + question*age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     cores = 8,
                     file = "cache/fit.brm.absence.difference")

fit.brm.absence.difference


df.data = expand_grid(age_float = seq(3, 9, 0.1),
                      question = c("cause", "lexical", "fault"))

df.prediction = fit.brm.absence.difference %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  clean_names()

df.linear = df.model %>% 
  mutate(participant_age = factor(participant_age, 
                            levels = c(3, 4, 5, 6, 7, 8, 9), 
                            labels = c("3", "4", "5", "6", "7", "8", "9")))

df.means = df.linear %>% 
  group_by(participant_age, question) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(participant_age = as.numeric(as.character(participant_age)))

p2 = ggplot(mapping = aes(x = age_float, 
                     y = difference,
                     color = question)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = participant_age,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = FALSE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.65)) +
  ylab(element_blank()) +
  scale_fill_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), breaks=c("cause", "lexical", "fault")) +
  scale_color_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), breaks=c("cause", "lexical", "fault")) +
  scale_shape_manual(values = c(23, 21, 24)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n direct", "75%", "50%", "75%", "100% \n absent"),
                     limits = c(0, 1)) + 
  scale_x_continuous(name = "Age",
                     breaks = 3:9,
                     labels = c("3", "4", "5", "6", "7", "8", "9")) +
  theme(plot.title = element_text(hjust = 1),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        legend.title = element_blank(),
        text = element_text(size = 20))

p2
```

# APPENDIX
## EXPERIMENT 1: CHAIN CASES
### STATS
#### Bayesian Models
##### Distal

```{r message=FALSE, warning=FALSE}

df.model = df.exp1_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, 
                           "fault",   
                           "cause", # second
                           "lexical"),  # etc...
         age_float = age_float - mean(age_float))

# Check contrast values
 contrasts(df.model$question)


fit.brm.cause.children.distal = brm(formula = distal ~ 1 + question + (1 | response_id) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_distal") 

fit.brm.cause.children.distal


fit.brm.cause.children.distal.age = brm(formula = distal ~ 1 + question*age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_distal_age") 

fit.brm.cause.children.distal.age 

```

##### Proximal
```{r message=FALSE, warning=FALSE}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.cause.children.proximal = brm(formula = proximal ~ 1 + question + (1 | response_id),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_proximal") 

fit.brm.cause.children.proximal


fit.brm.cause.children.proximal.age = brm(formula = proximal ~ 1 + question*age_float + (1 | response_id) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_proximal_age") 

fit.brm.cause.children.proximal.age


```

## PLOTS
### Caused vs. Lexical vs. Fault
```{r message=FALSE, warning=FALSE}

df.model = df.exp1_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, 
                               "fault",   
                               "cause", # second
                               "lexical"))

fit.brm.distal.cause.age2 = brm(formula = distal ~ 1 + question*age_float + (1 | response_id) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.distal.cause.age2")


fit.brm.proximal.cause.age2 = brm(formula = proximal ~ 1 + question*age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 6000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.proximal.cause.age2")

df.data = expand_grid(age_float = seq(3, 9, 0.1),
                      question = c("fault", "cause", "lexical"))

df.prediction = fit.brm.distal.cause.age2 %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  mutate(type = "distal") %>% 
  bind_rows(fit.brm.proximal.cause.age2 %>% 
              fitted(newdata = df.data,
                     re_formula = NA,
                     probs = c(0.1, 0.9)) %>% 
              as_tibble() %>% 
              bind_cols(df.data) %>% 
              mutate(type = "proximal")) %>% 
  clean_names()

df.children = df.exp1_children %>% 
  pivot_longer(cols = distal:proximal,
               names_to = "type",
               values_to = "response")

df.means = df.children %>% 
  mutate(participant_age = factor(participant_age, 
                            levels = c(3, 4, 5, 6, 7, 8, 9), 
                            labels = c("3", "4", "5", "6", "7", "8", "9")),
         question = recode(question, "cause" = "cause")) %>% 
  group_by(participant_age, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(participant_age = as.numeric(as.character(participant_age)))

df.means = df.means %>%
  mutate(question = factor(question, levels = c("cause", "lexical", "fault")))

custom_labels = as_labeller(c("distal" = "Distal Cause", "proximal" = "Proximal Cause"))

p3 = ggplot(mapping = aes(x = age_float, 
                     y = response,
                     color = question)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = participant_age,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.5)) +
    facet_wrap(~type,
             labeller = custom_labels) + 
  scale_fill_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), 
                    breaks=c("cause", "lexical", "fault")) +
  scale_color_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), 
                     breaks=c("cause", "lexical", "fault")) +
  scale_shape_manual(values = c(23, 21, 24)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%")) +
  scale_x_continuous(breaks = 3:9,
                     labels = c("3", "4", "5", "6", "7", "8", "9")) +
  labs(y = "Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) 

p3
```
## EXPERIMENT 2: ABSENCE CASES
### STATS
#### Bayesian Models
##### Absent

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, 
                           "fault",   
                           "cause", # second
                           "lexical"),  # etc...
         age_float = age_float - mean(age_float))

# Check contrast values
 contrasts(df.model$question)


fit.brm.cause.children.absent = brm(formula = absent ~ 1 + question + (1 | response_id) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_absent") 

fit.brm.cause.children.absent


fit.brm.cause.children.absent.age = brm(formula = absent ~ 1 + question*age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_absent_age") 

fit.brm.cause.children.absent.age 

```

##### Direct
```{r message=FALSE, warning=FALSE}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.cause.children.direct = brm(formula = direct ~ 1 + question + (1 | response_id),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_direct") 

fit.brm.cause.children.direct


fit.brm.cause.children.direct.age = brm(formula = direct ~ 1 + question*age_float + (1 | response_id) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_direct_age") 

fit.brm.cause.children.direct.age


```

## PLOTS
### Caused vs. Lexical vs. Fault
```{r message=FALSE, warning=FALSE}

df.model = df.exp2_children %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, 
                               "fault",   
                               "cause", # second
                               "lexical"))

fit.brm.absent.cause.age2 = brm(formula = absent ~ 1 + question*age_float + (1 | response_id) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.absent.cause.age2")


fit.brm.direct.cause.age2 = brm(formula = direct ~ 1 + question*age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 6000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.direct.cause.age2")

df.data = expand_grid(age_float = seq(3, 9, 0.1),
                      question = c("fault", "cause", "lexical"))

df.prediction = fit.brm.absent.cause.age2 %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  mutate(type = "absent") %>% 
  bind_rows(fit.brm.direct.cause.age2 %>% 
              fitted(newdata = df.data,
                     re_formula = NA,
                     probs = c(0.1, 0.9)) %>% 
              as_tibble() %>% 
              bind_cols(df.data) %>% 
              mutate(type = "direct")) %>% 
  clean_names()

df.children = df.exp2_children %>% 
  pivot_longer(cols = absent:direct,
               names_to = "type",
               values_to = "response")

df.means = df.children %>% 
  mutate(participant_age = factor(participant_age, 
                            levels = c(3, 4, 5, 6, 7, 8, 9), 
                            labels = c("3", "4", "5", "6", "7", "8", "9")),
         question = recode(question, "cause" = "cause")) %>% 
  group_by(participant_age, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(participant_age = as.numeric(as.character(participant_age)))

df.means = df.means %>%
  mutate(question = factor(question, levels = c("cause", "lexical", "fault")))

custom_labels = as_labeller(c("absent" = "Absent Cause", "direct" = "Direct Cause"))

p4 = ggplot(mapping = aes(x = age_float, 
                     y = response,
                     color = question)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = participant_age,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.5)) +
    facet_wrap(~type,
             labeller = custom_labels) + 
  scale_fill_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), 
                    breaks=c("cause", "lexical", "fault")) +
  scale_color_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), 
                     breaks=c("cause", "lexical", "fault")) +
  scale_shape_manual(values = c(23, 21, 24)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%")) +
  scale_x_continuous(breaks = 3:9,
                     labels = c("3", "4", "5", "6", "7", "8", "9")) +
  labs(y = "Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) 

p4
```


# SESSION INFO

```{r}
sessionInfo()
```
