---
title: "Causal verbs and responsibility"
author: "Cici Hou, David Rose & Ellen Markman"
date: "`r Sys.time()`"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 6
    toc_float: true
    theme: cosmo
    highlight: tango
---

# Load packages

```{r eval=TRUE, include=FALSE, message=FALSE, warning=FALSE}

library("tidytext")
library("xtable")          # for saving tables
library("janitor")         # for cleaning variable names
library("emmeans")         # for comparing means
library("brms")            # for Bayesian data analysis
library("patchwork")       # for combining figures
library("knitr")           # for knitting 
library("marginaleffects") # for marginal effects
library("ggtext")          # for adding text to figures
library("grid")            # for annotation custom
library("RColorBrewer")    # for colors 
library("ggtext")          # for text in ggplot 
library("tidyverse")       # for everything else
```

# Settings

```{r message=FALSE, warning=FALSE}

# set theme 
theme_set(theme_classic())

# suppress grouping warning 
options(dplyr.summarise.inform = F)
```


# EXPERIMENT 1: CHAIN CASES
## DATA
### Read in data
```{r message=FALSE, warning=FALSE}

df.exp1_children = read_csv("../../data/exp1_child_clean.csv") 

df.exp1_children = df.exp1_children %>%
  select(scenario_order, gender_order, question, participant_age, age_float, distal, proximal, scenario, response_id, gender, lan_spoken)

###check for duplicates####
duplicates_check = df.exp1_children %>%
  group_by(response_id) %>%
  summarise(row_count = n()) %>%
  filter(row_count != 6)

print(duplicates_check)

```



### Demographics

```{r message=FALSE, warning=FALSE}
# gender
df.exp1_children %>%
  group_by(gender) %>%
  summarise(n = n_distinct(response_id)) %>%
  print()

# language spoken
df.exp1_children %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(response_id)) %>%
    print()
```

## STATS

### Bayesian Model
```{r message=FALSE, warning=FALSE}
df.exp1_children_different = df.exp1_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))

df.exp1_children_both = df.exp1_children %>%
  mutate(response_pattern = case_when(
    distal == 1 & proximal == 1 ~ "both",
    distal == 0 & proximal == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both") 


 df.exp1_children_both = df.exp1_children_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.exp1_children_both %>% 
              mutate(difference = 0)) 

df.exp1_children_new = df.exp1_children_different %>% 
  bind_rows(df.exp1_children_both) 
  
df.model = df.exp1_children_new %>% 
  mutate(question = as_factor(question),
         question = fct_relevel(question, 
                                "fault",   
                                "cause", 
                                "lexical"))

fit.brm.chain.children = brm(formula = difference ~ 1 + question * age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/chain_cause_children_difference") 

fit.brm.chain.children 
```

### Follow-up analysis 

```{r}
# effect of question 
fit.brm.chain.children %>% 
  emmeans(spec = pairwise ~ question, 
          type = "response")

# effect of age
fit.brm.chain.children %>%
  avg_slopes(variable = "age_float",
             type = "link")
  
# interaction effect 
fit.brm.chain.children %>% 
  emtrends(specs = pairwise ~ question,
           var = "age_float")
```

### Means and Confidence Interval  

```{r}

df.exp1_children_new %>% 
  group_by(question) %>% 
  summarise(
    mean = mean(difference),
    ci_lower = mean_cl_normal(difference)$ymin,
    ci_upper = mean_cl_normal(difference)$ymax
  )

```

## PLOTS
### Overall Responses by Age

```{r message=FALSE, warning=FALSE}

df.model = df.exp1_children_new %>% 
  mutate(difference = distal - proximal,
        difference = recode(difference, `-1` = 0))

fit.brm.chain.difference = brm(formula = difference ~ 1 + question*age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     cores = 8,
                     file = "cache/fit.brm.chain.difference")

fit.brm.chain.difference

df.data = expand_grid(age_float = seq(3, 9, 0.1),
                      question = c("cause", "lexical", "fault"))

df.prediction = fit.brm.chain.difference %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  clean_names()

df.linear = df.model %>% 
  mutate(participant_age = factor(participant_age, 
                            levels = c(3, 4, 5, 6, 7, 8, 9), 
                            labels = c("3", "4", "5", "6", "7", "8", "9")))

df.means = df.linear %>% 
  group_by(participant_age, question) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(participant_age = as.numeric(as.character(participant_age)))

p1 = ggplot(mapping = aes(x = age_float, 
                     y = difference,
                     color = question)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = participant_age,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = FALSE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.5)) +
  ylab(element_blank()) +
  scale_fill_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), 
                    breaks=c("cause", "lexical", "fault"),
                    labels = c("caused", "fault", "lexical")) +
  scale_color_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), 
                     breaks=c("cause", "lexical", "fault"),
                     labels = c("caused", "fault", "lexical")) +
  scale_shape_manual(values = c(23, 21, 24)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n proximal", "75%", "50%", "75%", "100% \n distal"),
                     limits = c(0, 1)) + 
  scale_x_continuous(name = "Age",
                     breaks = 3:9,
                     labels = c("3", "4", "5", "6", "7", "8", "9")) +
  theme(plot.title = element_text(hjust = 1),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        legend.title = element_blank(),
        text = element_text(size = 20))

p1
```

### Responses Patterns by Age

```{r} 

df.plot = df.exp1_children %>% 
  pivot_wider(names_from = question,
              values_from = c(distal, proximal)) %>% 
  pivot_longer(cols = distal_cause:proximal_fault,
               names_to = c("type", ".value"),
               names_sep = "_") %>% 
  mutate(response_pattern = case_when(
    cause == 0 & fault == 0 & lexical == 0 ~ "none",
    cause == 0 & fault == 0 & lexical == 1 ~ "lexical only",
    cause == 0 & fault == 1 & lexical == 0 ~ "fault only",
    cause == 1 & fault == 0 & lexical == 0 ~ "cause only",
    cause == 0 & fault == 1 & lexical == 1 ~ "lexical + fault",
    cause == 1 & fault == 0 & lexical == 1 ~ "lexical + cause",
    cause == 1 & fault == 1 & lexical == 0 ~ "cause + fault",
    cause == 1 & fault == 1 & lexical == 1 ~ "all"))


###########STOPPED HERE###########

  
  
  
  


# df.plot = df.exp1_children %>% 
#   mutate(response_pattern = case_when(
#     distal == 1 & proximal == 1 ~ "both",
#     distal == 0 & proximal == 0 ~ "neither",
#     distal == 1 & proximal == 0  ~ "distal only",
#     distal == 0 & proximal == 1  ~ "proximal only",
#   ),
#   question = recode(question, "cause" = "caused"),
#   age_whole = as.factor(as.integer(age_float))) %>% 
#   group_by(age_whole, question, response_pattern) %>% 
#   summarize(n = n()) %>% 
#   ungroup() %>%
#   group_by(age_whole, question) %>%
#   mutate(percentage = n / sum(n) * 100) %>%
#   ungroup() %>% 
#   mutate(question = factor(question, levels = c("caused", "fault", "lexical")),
#          response_pattern = factor(response_pattern, levels = c("distal only", "proximal only", "both", "neither")))
# 
# 
# df.labels = df.plot %>% 
#   group_by(age_whole, question) %>%
#   summarize(count = sum(n)/2) %>% 
#   ungroup() %>% 
#   mutate(age = as.character(factor(age_whole,
#                                    levels = c(3, 4, 5, 6, 7, 8, 9),
#                                    labels = c("3", "4", "5", "6", "7", "8", "9"))),
#          count = ifelse(question == "lexical" & age_whole == 3, str_c("n=", count), count),
#          label = str_c("<span style='font-size:16px;'>", age, "</span>"),
#          label = ifelse(question == "lexical", 
#                         str_c("<span style='font-size:16px;'>", age, "</span>", "<br>",
#                               "<span style='font-size:12px;'>(", count, ")", "</span>"), label),
#          question = factor(question, levels = c("caused", "fault", "lexical")))
# 
# df.plot = df.plot %>% 
#   left_join(df.labels %>% 
#               select(age_whole, question, label), 
#             by = c("age_whole", "question")) %>% 
#   mutate(label = factor(label, levels = df.labels$label))
# 
# 
# p2 = ggplot(data = df.plot,
#             mapping = aes(x = label,
#                           y = percentage,
#                           group = response_pattern,
#                           color = response_pattern,
#                           fill = response_pattern)) +
#   geom_col(color = "black") +
#   facet_wrap(~question, 
#              scales = "free_x") + 
#   scale_fill_manual(values = c("distal only" = "#FF7F00",
#                                "proximal only" = "#FFFF33",
#                                "both" = "#984EA3",
#                                "neither" = "#999999")) +
#   scale_color_manual(values = c("distal only" = "#FF7F00",
#                                 "proximal only" = "#FFFF33",
#                                 "both" = "#984EA3",
#                                 "neither" = "#999999")) +
#   scale_shape_manual(values = c(21, 23)) +
#   scale_y_continuous(breaks = seq(0, 100, 25),
#                      labels = str_c(seq(0, 100, 25), "%"),
#                      expand = expansion(add = c(0, 0))) +
#   scale_x_discrete(expand = expansion(add = c(0, 0))) +
#   coord_cartesian(clip = "off") +
#   labs(y = "Response pattern \n\ probability") +
#   theme(legend.position = "bottom",
#         legend.title = element_blank(),
#         legend.text = element_text(size = 14),
#         axis.text.y = element_text(size = 12),
#         axis.title.y = element_text(size = 16),
#         axis.text.x = element_markdown(),
#         axis.title.x = element_blank(),
#         strip.background = element_blank(),
#         strip.text = element_blank(),
#         panel.spacing = unit(.4, "cm"))
# 
# p2


```




# EXPERIMENT 2: ABSENCE CASES
## DATA
### Read in data
```{r}
df.exp2_children = read_csv("../../data/exp2_child_clean.csv") 

df.exp2_children = df.exp2_children %>%
  select(scenario_order, gender_order, question, participant_age, age_float, direct, absent, scenario, response_id, gender, lan_spoken)

duplicates_check <- df.exp2_children %>%
  group_by(response_id) %>%
  summarise(row_count = n()) %>%
  filter(row_count != 6)

print(duplicates_check)
```
### Demographics

```{r message=FALSE, warning=FALSE}
# gender
df.exp2_children %>%
  group_by(gender) %>%
  summarise(n = n_distinct(response_id)) %>%
  print()

# language spoken
df.exp2_children %>%
    mutate(en_occurrence = ifelse(str_detect(lan_spoken, "en"), "en", "non-en")) %>%
    group_by(en_occurrence) %>%
    summarise(n = n_distinct(response_id)) %>%
    print()
```

## STATS

### Bayesian Model
```{r message=FALSE, warning=FALSE}
df.exp2_children_different = df.exp2_children %>%
  mutate(response_pattern = case_when(
    absent == 1 & direct == 1 ~ "both",
    absent == 0 & direct == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "different") %>%
  mutate(difference = absent - direct,
        difference = recode(difference, `-1` = 0))

df.exp2_children_both = df.exp2_children %>%
  mutate(response_pattern = case_when(
    absent == 1 & direct == 1 ~ "both",
    absent == 0 & direct == 0 ~ "neither",
    TRUE ~ "different"
  )) %>%
  filter(response_pattern == "both") 


 df.exp2_children_both = df.exp2_children_both %>% 
  mutate(difference = 1) %>%
  bind_rows(df.exp2_children_both %>% 
              mutate(difference = 0)) 

df.exp2_children_new = df.exp2_children_different %>% 
  bind_rows(df.exp2_children_both) 
  
df.model = df.exp2_children_new %>% 
  mutate(
    # Convert to factor explicitly
    question = as_factor(question),
    question = fct_relevel(question, 
                           "fault",   
                           "cause", # second
                           "lexical")  # etc...
  )

fit.brm.absence.children = brm(formula = difference ~ 1 + question * age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     file = "cache/absence_cause_children_difference") 

fit.brm.absence.children 
```

### Follow-up analysis 

```{r}
# effect of question 
fit.brm.absence.children %>% 
  emmeans(spec = pairwise ~ question, 
          type = "response")
# 
# # effect of age
# fit.brm.absence.children %>%
#   avg_slopes(variable = "age_float",
#              type = "link")
  
# interaction effect 
fit.brm.absence.children %>% 
  emtrends(specs = pairwise ~ question,
           var = "age_float")
```

### Means and Confidence Interval  

```{r}

df.exp2_children_new %>% 
  group_by(question) %>% 
  summarise(
    mean = mean(difference),
    ci_lower = mean_cl_normal(difference)$ymin,
    ci_upper = mean_cl_normal(difference)$ymax
  )

```

## PLOTS
### Overall Responses by Age

```{r}

df.model = df.exp2_children_new %>%
  mutate(difference = absent - direct,
        difference = recode(difference, `-1` = 0))

fit.brm.absence.difference = brm(formula = difference ~ 1 + question*age_float + (1 | response_id) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     cores = 8,
                     file = "cache/fit.brm.absence.difference")

fit.brm.absence.difference


df.data = expand_grid(age_float = seq(3, 9, 0.1),
                      question = c("cause", "lexical", "fault"))

df.prediction = fit.brm.absence.difference %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  clean_names()

df.linear = df.model %>% 
  mutate(participant_age = factor(participant_age, 
                            levels = c(3, 4, 5, 6, 7, 8, 9), 
                            labels = c("3", "4", "5", "6", "7", "8", "9")))

df.means = df.linear %>% 
  group_by(participant_age, question) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(difference)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(participant_age = as.numeric(as.character(participant_age)))

p3 = ggplot(mapping = aes(x = age_float, 
                     y = difference,
                     color = question)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = participant_age,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = FALSE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.65)) +
  ylab(element_blank()) +
    scale_fill_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), 
                    breaks=c("cause", "lexical", "fault"),
                    labels = c("caused", "lexical", "fault")) +
  scale_color_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), 
                     breaks=c("cause", "lexical", "fault"),
                     labels = c("caused", "lexical", "fault")) +
  scale_shape_manual(values = c(23, 21, 24)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = c("100% \n direct", "75%", "50%", "75%", "100% \n absent"),
                     limits = c(0, 1)) + 
  scale_x_continuous(name = "Age",
                     breaks = 3:9,
                     labels = c("3", "4", "5", "6", "7", "8", "9")) +
  labs(y = "Probability of selecting \n direct or absent cause") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        legend.text = element_text(size = 14),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 16))

```

### Responses Patterns by Age

```{r message=FALSE, warning=FALSE}

df.plot = df.exp2_children %>% 
  pivot_wider(names_from = question,
              values_from = c(direct, absent)) %>% 
  pivot_longer(cols = direct_cause:absent_fault,
               names_to = c("type", ".value"),
               names_sep = "_") %>% 
  mutate(response_pattern = case_when(
    cause == 0 & fault == 0 & lexical == 0 ~ "none",
    cause == 0 & fault == 0 & lexical == 1 ~ "lexical only",
    cause == 0 & fault == 1 & lexical == 0 ~ "fault only",
    cause == 1 & fault == 0 & lexical == 0 ~ "caused only",
    cause == 0 & fault == 1 & lexical == 1 ~ "lexical + fault",
    cause == 1 & fault == 0 & lexical == 1 ~ "caused + lexical",
    cause == 1 & fault == 1 & lexical == 0 ~ "caused + fault",
    cause == 1 & fault == 1 & lexical == 1 ~ "all")) %>% 
  group_by(participant_age, type, response_pattern) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  group_by(participant_age, type) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup() %>%
  mutate(type = factor(type, levels = c("direct", "absent")),
         response_pattern = factor(response_pattern, levels = c("caused only", "lexical only", "fault only", "caused + lexical", "caused + fault", "lexical + fault",  "all", "none")))


df.labels = df.plot %>%
  group_by(participant_age, type) %>%
  summarize(count = sum(n)/2) %>%
  ungroup() %>%
  mutate(age = as.character(factor(participant_age,
                                   levels = c(3, 4, 5, 6, 7, 8, 9),
                                   labels = c("3", "4", "5", "6", "7", "8", "9"))),
         count = ifelse(type == "direct" & participant_age == 3, str_c("n=", count), count),
         label = str_c("<span style='font-size:16px;'>", age, "</span>"),
         label = ifelse(type == "direct",
                        str_c("<span style='font-size:16px;'>", age, "</span>", "<br>",
                              "<span style='font-size:12px;'>(", count, ")", "</span>"), label),
         type = factor(type, levels = c("direct", "absent")))



df.plot = df.plot %>%
  left_join(df.labels %>%
              select(participant_age, type, label),
            by = c("participant_age", "type")) %>%
  mutate(label = factor(label, levels = df.labels$label))



p4 = ggplot(data = df.plot,
            mapping = aes(x = label,
                          y = percentage,
                          group = response_pattern,
                          color = response_pattern,
                          fill = response_pattern)) +
  geom_col(color = "black") +
  facet_wrap(~type,
             scales = "free_x") +
    scale_fill_manual(values = c("caused only" = "#dc3410",
                               "fault only" = "#4DAF4A",
                               "lexical only" = "#377EB8",
                               "caused + fault" = "#A0522D",
                               "lexical + fault" = "#40E0D0",
                               "caused + lexical" = "#800080",
                               "all" = "#FFFFFF",
                               "none" = "#000000")) +
  scale_color_manual(values = c("caused only" = "#dc3410",
                               "fault only" = "#4DAF4A",
                               "lexical only" = "#377EB8",
                               "caused + fault" = "#A0522D",
                               "lexical + fault" = "#40E0D0",
                               "caused + lexical" = "#800080",
                               "all" = "#FFFFFF")) +
  # scale_fill_manual(values = c("caused only" = "#FF7F00",
  #                              "fault only" = "#800080",
  #                              "lexical only" = "#FFFF33",
  #                              "caused + fault" = "#CC527A",
  #                              "lexical + fault" = "#C66900",
  #                              "caused + lexical" = "#FFB74D",
  #                              "all" = "#A0522D",
  #                              "none" = "#999999")) +
  # scale_color_manual(values = c("caused only" = "#FF7F00",
  #                              "fault only" = "#800080",
  #                              "lexical only" = "#FFFF33",
  #                              "caused + fault" = "#CC527A",
  #                              "lexical + fault" = "#C66900",
  #                              "caused + lexical" = "#FFB74D",
  #                              "all" = "#A0522D",
  #                              "none" = "#999999")) +
  scale_shape_manual(values = c(21, 23)) +
  scale_y_continuous(breaks = seq(0, 100, 25),
                     labels = str_c(seq(0, 100, 25), "%"),
                     expand = expansion(add = c(0, 0))) +
  scale_x_discrete(expand = expansion(add = c(0, 0))) +
  coord_cartesian(clip = "off") +
  labs(y = "Response pattern \n\ probability") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        legend.text = element_text(size = 14),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 16),
        axis.text.x = element_markdown(),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(size = 16),
        panel.spacing = unit(.4, "cm")) +
 guides(fill = guide_legend(order = 1, nrow = 2, byrow = TRUE,
                             override.aes = list(order = c(1, 3, 2, 6, 4, 5, 7, 8))),
         color = guide_legend(order = 1, nrow = 2, byrow = TRUE,
                              override.aes = list(order = c(1, 3, 2, 6, 4, 5, 7, 8))))

p4

```

### Combine Plots

```{r fig.height=5.5, fig.width=13, message=FALSE, warning=FALSE}

design = "
122
"    

plot = wrap_plots(
  A = p3,
  B = p4,
  design = design
) + 
  plot_annotation(tag_levels = "A") &
  theme(plot.tag = element_text(face = "bold"))


ggsave(plot, filename = "../../figures/experiment2/exp2_plot.pdf", height = 5.5, width = 13)


plot

```

# APPENDIX
## EXPERIMENT 1: CHAIN CASES
### STATS
#### Bayesian Models
##### Distal

```{r message=FALSE, warning=FALSE}

df.model = df.exp1_children %>% 
  filter(age_float >= 4, age_float <= 9) %>%
  mutate(question = as_factor(question),
         question = fct_relevel(question, 
                                "lexical", "fault", "cause"),  # etc...
         age_float = age_float - mean(age_float))
# Check contrast values
 contrasts(df.model$question)


fit.brm.cause.children.distal = brm(formula = distal ~ 1 + question + (1 | response_id) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_distal") 

fit.brm.cause.children.distal


fit.brm.cause.children.distal.age = brm(formula = distal ~ 1 + question*age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_distal_age") 

fit.brm.cause.children.distal.age 

```

##### Proximal
```{r message=FALSE, warning=FALSE}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.cause.children.proximal = brm(formula = proximal ~ 1 + question + (1 | response_id),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_proximal") 

fit.brm.cause.children.proximal


fit.brm.cause.children.proximal.age = brm(formula = proximal ~ 1 + question*age_float + (1 | response_id) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_proximal_age") 

fit.brm.cause.children.proximal.age


```

### PLOTS
#### Caused vs. Lexical vs. Fault
```{r message=FALSE, warning=FALSE}

df.model = df.exp1_children %>% 
  filter(age_float >= 4, age_float <= 9) %>%
  mutate(question = as_factor(question),
         question = fct_relevel(question, 
                               "lexical"))

fit.brm.distal.cause.age2 = brm(formula = distal ~ 1 + question*age_float + (1 | response_id) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.distal.cause.age2")


fit.brm.proximal.cause.age2 = brm(formula = proximal ~ 1 + question*age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 6000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.proximal.cause.age2")

df.data = expand_grid(age_float = seq(4, 9, 0.1),
                      question = c("fault", "cause", "lexical"))

df.prediction = fit.brm.distal.cause.age2 %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  mutate(type = "distal") %>% 
  bind_rows(fit.brm.proximal.cause.age2 %>% 
              fitted(newdata = df.data,
                     re_formula = NA,
                     probs = c(0.1, 0.9)) %>% 
              as_tibble() %>% 
              bind_cols(df.data) %>% 
              mutate(type = "proximal")) %>% 
  clean_names()

df.children = df.exp1_children %>% 
  pivot_longer(cols = distal:proximal,
               names_to = "type",
               values_to = "response")

df.means = df.children %>% 
  mutate(participant_age = factor(participant_age, 
                            levels = c(4, 5, 6, 7, 8, 9), 
                            labels = c("4", "5", "6", "7", "8", "9")),
         question = recode(question, "cause" = "cause")) %>% 
  group_by(participant_age, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(participant_age = as.numeric(as.character(participant_age)))

df.means = df.means %>%
  mutate(question = factor(question, levels = c("cause", "lexical", "fault")))

custom_labels = as_labeller(c("distal" = "Distal Cause", "proximal" = "Proximal Cause"))

p3 = ggplot(mapping = aes(x = age_float, 
                     y = response,
                     color = question)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = participant_age,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.5)) +
    facet_wrap(~type,
             labeller = custom_labels) + 
  scale_fill_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), 
                    breaks=c("cause", "lexical", "fault")) +
  scale_color_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), 
                     breaks=c("cause", "lexical", "fault")) +
  scale_shape_manual(values = c(23, 21, 24)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%")) +
  scale_x_continuous(breaks = 4:9,
                     labels = c("4", "5", "6", "7", "8", "9")) +
  labs(y = "Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) 

p3
```

## EXPERIMENT 2: ABSENCE CASES
### STATS
#### Bayesian Models
##### Absent

```{r message=FALSE, warning=FALSE}

df.model = df.exp2_children %>% 
  filter(age_float >= 4, age_float <= 9) %>%
  mutate(question = as_factor(question),
         question = fct_relevel(question, 
                                "lexical", "fault", "cause"),  # etc...
         age_float = age_float - mean(age_float))

# Check contrast values
 contrasts(df.model$question)


fit.brm.cause.children.absent = brm(formula = absent ~ 1 + question + (1 | response_id) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_absent") 

fit.brm.cause.children.absent


fit.brm.cause.children.absent.age = brm(formula = absent ~ 1 + question*age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .999999),
                     file = "cache/cause_children_absent_age") 

fit.brm.cause.children.absent.age 

```

##### Direct
```{r message=FALSE, warning=FALSE}

# removed random intercepts for scenario to avoid divergent transition errors
fit.brm.cause.children.direct = brm(formula = direct ~ 1 + question + (1 | response_id),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_direct") 

fit.brm.cause.children.direct


fit.brm.cause.children.direct.age = brm(formula = direct ~ 1 + question*age_float + (1 | response_id) + (1 | scenario),
                      data = df.model,
                      family = "bernoulli",
                      seed = 1,
                      iter = 4000,
                      warmup = 1000,
                      control = list(adapt_delta = .999999),
                      file = "cache/cause_children_direct_age") 

fit.brm.cause.children.direct.age


```

### PLOTS
#### Caused vs. Lexical vs. Fault
```{r message=FALSE, warning=FALSE}

df.model = df.exp2_children %>% 
  filter(age_float >= 4, age_float <= 9) %>%
  mutate(question = as_factor(question),
         question = fct_relevel(question, 
                               "lexical"))

fit.brm.absent.cause.age2 = brm(formula = absent ~ 1 + question*age_float + (1 | response_id) + (1 | scenario),
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 4000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.absent.cause.age2")


fit.brm.direct.cause.age2 = brm(formula = direct ~ 1 + question*age_float + (1 | response_id) + (1 | scenario), 
                     data = df.model,
                     family = "bernoulli",
                     seed = 1,
                     iter = 6000,
                     warmup = 1000,
                     control = list(adapt_delta = .9999),
                     file = "cache/fit.brm.direct.cause.age2")

df.data = expand_grid(age_float = seq(3, 9, 0.1),
                      question = c("fault", "cause", "lexical"))

df.prediction = fit.brm.absent.cause.age2 %>% 
  fitted(newdata = df.data,
         re_formula = NA,
          probs = c(0.1, 0.9)) %>% 
  as_tibble() %>% 
  bind_cols(df.data) %>% 
  mutate(type = "absent") %>% 
  bind_rows(fit.brm.direct.cause.age2 %>% 
              fitted(newdata = df.data,
                     re_formula = NA,
                     probs = c(0.1, 0.9)) %>% 
              as_tibble() %>% 
              bind_cols(df.data) %>% 
              mutate(type = "direct")) %>% 
  clean_names()

df.children = df.exp2_children %>% 
  pivot_longer(cols = absent:direct,
               names_to = "type",
               values_to = "response")

df.means = df.children %>% 
  mutate(participant_age = factor(participant_age, 
                            levels = c(3, 4, 5, 6, 7, 8, 9), 
                            labels = c("3", "4", "5", "6", "7", "8", "9")),
         question = recode(question, "cause" = "cause")) %>% 
  group_by(participant_age, question, type) %>% 
  summarize(
    response = Hmisc::smean.cl.boot(response)) %>%
    mutate(index = c("response", "low", "high")) %>%
    ungroup() %>% 
    pivot_wider(names_from = index,
                values_from = response) %>% 
  mutate(participant_age = as.numeric(as.character(participant_age)))

df.means = df.means %>%
  mutate(question = factor(question, levels = c("cause", "lexical", "fault")))

custom_labels = as_labeller(c("absent" = "Absent Cause", "direct" = "Direct Cause"))

p4 = ggplot(mapping = aes(x = age_float, 
                     y = response,
                     color = question)) + 
  geom_hline(yintercept=0.50, linetype="dashed", color = "black") +
  geom_smooth(data = df.prediction,
              mapping = aes(y = estimate,
                            ymin = q10,
                            ymax = q90,
                            color = question,
                            fill = question),
              stat = "identity",
              alpha = 0.2,
              show.legend = F) +
  geom_pointrange(data = df.means,
                  mapping = aes(x = participant_age,
                                y = response,
                                ymin = low,
                                ymax = high,
                                fill = question,
                                shape = question),
                  color = "black",
                  size = 0.5,
                  show.legend = TRUE,
                  alpha = 0.8,
                  position = position_dodge(width = 0.5)) +
    facet_wrap(~type,
             labeller = custom_labels) + 
  scale_fill_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), 
                    breaks=c("cause", "lexical", "fault")) +
  scale_color_manual(values = c("cause" = "#dc3410", "lexical" = "#377EB8", "fault" = "#4DAF4A"), 
                     breaks=c("cause", "lexical", "fault")) +
  scale_shape_manual(values = c(23, 21, 24)) +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                      labels = str_c(seq(0, 1, 0.25) * 100, "%")) +
  scale_x_continuous(breaks = 3:9,
                     labels = c("3", "4", "5", "6", "7", "8", "9")) +
  labs(y = "Probability of selecting \n causal candidate") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        text = element_text(size = 18)) 

p4
```


# SESSION INFO

```{r}
sessionInfo()
```
